Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-11 documentation/paper.tex
Added histograms for supervised learning techniques

However, the lack of decisiveness observed even when accuracy was relatively high implies that, without $WallCut(D)$, this is a suboptimal technique.

@@

It became evident very quickly that, without $WallCut(D)$, a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Increasing the number of bands to $FourierMLPWithPos(beta_{20}, \chi)$, did not improve the results; accuracy only reached 95\%, with an increased mean standard deviation of 0.42. 40 bands reduced the accuracy once again, to 91\%.

@@

The higher resolution demonstrated significant power when $WallCut(D)$ was not applied, and only \\ $QualCut(MultiCut(D))$ was used. $FourierMLPWithPos(\beta_{20}, \chi)$ achieved only 92\% accuracy (2 percentage points lower than the same configuration without $WallCut(D)$). However, training on $\beta_{50,001}$, which does not incorporate any banding, improved this figure to a maximum of 97\%. However, that epoch had a relatively high standard deviation, at 0.47.

@@

Throughout a variety of different network architectures, the best validation accuracy obtained was a deceptively high 85\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place. Also, the class-wise standard deviation was a very high 0.95, which implies its decisions are nearly random. It is likely fitting on some form of noise within $\iota$. The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

@@

The following tables compare the accuracy and mean class-wise standard deviation values of certain highlight supervised learning configurations with multiple input formats, with Acoustic Parameter and the original PICO-60 neural network provided as baselines.

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLP(PosCor(\beta_{8}), \chi)$ & 97\% & 0.42 \\
    \hline
    $FourierMLP(\beta_{8})$ & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 91\% & 0.53 \\
    \hline
    Original PICO-60 Neural Network & 94\% & 0.99 \\
    \hline
    Acoustic Parameter & N/A & 0.56 \\
    \hline
\end{tabular}

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 0.47 \\
    \hline
    $DeepConv(\omega)$ & 77\% & 0.86 \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
    \hline
    $ImageConv(\iota)$ & 85\% & 0.95 \\
    \hline
    Acoustic Parameter & N/A & 0.73 \\
    \hline
\end{tabular}

>>>>

However, there is a lack of decisiveness observed even when accuracy was relatively high, in Figure \ref{waveform_hist}. This implies that, without $WallCut(D)$, this is a suboptimal technique.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConvWithPos(\omega, \chi)$ discriminator.}
\end{figure}

@@

It became evident very quickly that, without $WallCut(D)$, a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}. Increasing the number of bands to $FourierMLPWithPos(beta_{20}, \chi)$, did not improve the results; accuracy only reached 95\%, with an increased mean standard deviation of 0.42. 40 bands reduced the accuracy once again, to 91\%.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{banded_no_pos_input_hist}
    \caption{\label{banded_no_pos_input_hist} Prediction distribution of the best $FourierMLP(\beta_{8})$ discriminator, with $WallCut(D)$.}
\end{figure}

@@

The higher resolution demonstrated significant power when $WallCut(D)$ was not applied, and only \\ $QualCut(MultiCut(D))$ was used. $FourierMLPWithPos(\beta_{20}, \chi)$ achieved only 92\% accuracy (2 percentage points lower than the same configuration without $WallCut(D)$). However, training on $\beta_{50,001}$, which does not incorporate any banding, improved this figure to a maximum of 97\%. However, that epoch had a relatively high class-wise standard deviation, at 0.47, as seen in Figure \ref{high_freq_no_wall_hist}.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{high_freq_no_wall_hist}
    \caption{\label{high_freq_no_wall_hist} Prediction distribution of the best $FourierMLPWithPos(\beta_{50,001}, \chi)$ discriminator, without $WallCut(D)$.}
\end{figure}

@@

Throughout a variety of different network architectures, the best validation accuracy obtained was a deceptively high 85\%. The corresponding training accuracy of 100\% indicates that severe overfitting is taking place. Also, the class-wise standard deviation was a very high 0.95, which implies its decisions are nearly random (as seen in Figure \ref{image_hist}). It is likely fitting on some form of noise within $\iota$. The fact that throughout many trials (including a grid search), no good performance on validation data was observed, provides significant evidence that images provide insufficient information for effective discrimination.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{image_hist}
    \caption{\label{image_hist} Prediction distribution of the best $ImageConv(\iota)$ discriminator.}
\end{figure}

@@

The following tables compare the accuracy and mean class-wise standard deviation values of certain highlight supervised learning configurations with multiple input formats, with the original PICO-60 neural network provided as a baseline.

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLP(PosCor(\beta_{8}), \chi)$ & 97\% & 0.42 \\
    \hline
    $FourierMLP(\beta_{8})$ & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 91\% & 0.53 \\
    \hline
    Original PICO-60 Neural Network & 94\% & 0.99 \\
    \hline
\end{tabular}

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 0.47 \\
    \hline
    $DeepConv(\omega)$ & 77\% & 0.86 \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
    \hline
    $ImageConv(\iota)$ & 85\% & 0.95 \\
    \hline
\end{tabular}
